\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{parskip}
\geometry{margin=1in}

\setlist[itemize]{left=0pt, label=--, labelsep=5pt}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    urlcolor=blue,
    citecolor=blue
}

\begin{document}

\begin{center}
\end{center}

\vspace{3pt}
\hrule

\vspace{1pt}
University student with hands-on experience in developing and maintaining software using modern technologies such as JavaScript, TypeScript, React.js, Rust, and Golang. Seeking an internship role to continue growing my skills in building and maintaining scalable, high-performance software.
\vspace{5pt}

\hrule
\vspace{5pt}

\section*{Projects}
\textbf{Webalyze} \hfill \textit{\href{http://github.com/quantinium03/webalyze}{github}} \\
\textit{python, beautifulsoup, playwright, langchain} \\
\vspace{-15pt}
\begin{itemize}[itemsep=0pt, parsep=0pt]
    \item Developed a Python-based web scraping tool using Playwright and BeautifulSoup to extract and analyze website data in real-time.
    \item Real-time analysis of website data by web scraping to deliver the most up-to-date and well-informed insights.
    \item Supports custom queries to transform data according to users will.
    \item Integrated local llms to provide dynamic responses, including summaries, tables, and detailed analyses.
\end{itemize}

\textbf{Asami} \hfill \textit{\href{http://asami.vercel.app}{asami}} \\
\textit{ReactJS} \\
\vspace{-15pt}
\begin{itemize}[itemsep=0pt, parsep=0pt]
    \item Developed an ASCII art generator that converts images or text into creative ASCII art representations.  
    \item Supports customizable output options, including font size, character sets to meet user preferences.  
    \item Implemented efficient algorithms for fast and accurate conversion of images into ASCII art while maintaining the original content's essence.  
\end{itemize}

\textbf{Lucy} \hfill \textit{\href{http://github.com/quantinium03/lucy}{github}} \\
\textit{Golang, Rust} \\
\vspace{-15pt}
\begin{itemize}[itemsep=0pt, parsep=0pt]
    \item Designed and developed a backend system to track keyboard input, mouse input, music being played, and activities in Neovim using the WakaTime API.  
    \item Implemented the backend using Golang, ensuring efficient data handling and processing.  
    \item Built a Rust-based frontend for input tracking, focusing on performance and real-time data collection.  
    \item Optimized the system for accuracy, reliability, and minimal resource consumption to maintain seamless tracking.  
\end{itemize}

\textbf{Lated} \hfill \textit{\href{http://github.com/quantinium03/lated}{github} | \href{http://lated.vercel.app}{lated}} \\
\textit{ReactJS, ExpressJS, JavaScript/TypeScript} \\
\vspace{-15pt}
\begin{itemize}[itemsep=0pt, parsep=0pt]
    \item Developed a feature-rich LaTeX editor with a React.js frontend, offering real-time preview and syntax highlighting for seamless document creation.
    \item Integrated Vim mode support, providing a tailored experience for power users familiar with keyboard based navigation.
    \item Implemented backend using ExpressJS to recieve latex and compile it to pdf to show on the frontend.
\end{itemize}

\vspace{5pt}
\hrule
\vspace{5pt}

% Skills
\section*{Skills}
\begin{itemize}[itemsep=0pt, parsep=0pt]
    \item \textbf{Languages:} HTML, CSS, JavaScript, TypeScript, Golang, Rust, C++, Python and Java, Nix
    \item \textbf{Frameworks:} TailwindCSS, ReactJS, NextJS, ExpressJS, Echo, Go-Fiber, NodeJS, Astro, React-Router.
    \item \textbf{Database and ORMS:} Postgres, Firebase, Gorm, SQLite, MongoDB, Sqlx.
    \item \textbf{Tools:} Git, Github, Neovim, VSCode, Docker, Pages, AWS S3.
    \item \textbf{Operating Systems:} Windows, Debian, Arch Linux, Ubuntu, NixOS
\end{itemize}
\vspace{5pt}

\hrule
\vspace{5pt}

% Education

\end{document}

